\documentclass[twocolumn]{article}
\usepackage{hyperref}
\usepackage{titling}
\usepackage{graphicx}

\DeclareGraphicsExtensions{.png}

\setlength{\droptitle}{-10em}

%opening
\title{Run On}
\author{Insert Catchy Tagline Here}
\date{}

\begin{document}

\maketitle

\section*{Authors}

\emph{Run On} was created by Jeremy Astolfi, Sam Handrick, Liam Middlebrook, and Chris Trantas

\section*{Premise}

Insert premise for the game here.

\section*{Materials}

\begin{itemize}
	\item Start Deck
	\item Middle Deck
	\item End Deck
\end{itemize}

\section*{Setup}

Shuffle the three decks separately and give each player 5 "Middle Cards." The player who has been awake the longest at this time becomes the first "Judge" of the game.

The judge will select two random cards from the "Start" and "End" decks respectively. Position the two cards between all players with the "Start" card on the left and the "End" card on the right, with a gap in the middle to place winning "Middle Card".

The "Start" card includes two characters set as (C1) and (C2), as well as a blank space set as (C3). The judge chooses any character they want to act as the (C3) character. All further of references to (C1), (C2), (C3) will refer to these characters.

Now the judge position alternates to the next player clockwise and the first round begins.

\subsection*{Normal Play}

At the beginning of each round every player other than the judge will play down a "Middle" card from their hand. Once all of the players have placed cards the judge will reveal the card, and chooses the one that best continues the story up to that point and adds it to the current story. All other "Middle" cards played that round will be placed in the discard pile.

Once the judge has picked a winning "Middle" card, all of the players whose cards were not chosen will draw another "Middle" card from the deck. If the winning player of that round has no cards remaining then they are declared the winner. At the end of each game the winner must read out the story that was created using the Start and End cards and all winnnig Middle cards.

If the Middle deck is exhausted, shuffle the discard pile and set it as the new Middle deck.

\section*{License}

This document and any related materials are released under the Creative Commons BY-SA 3.0 US license. A human readable summary and the full text for this license may be found at \url{https://creativecommons.org/licenses/by-sa/3.0/us/}.

\end{document}
